Template for indicator documentation

### 2023-09-14 slitasje.Rmd
Fix #116

```{r extrapolated-slitasje, fig.cap="Slitasje indicator extrapolated over Trondheim"}
myCol <- "RdYlGn"
tmap_arrange(
tm_shape(wetlands_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Wetland"),

>>>>

```{r extrapolated-slitasje, fig.cap="Slitasje indicator extrapolated over Trondheim, with one map for each ecosystem. The map is not masked against ecosystem delineation maps, which make them easy to missinterpret."}
myCol <- "RdYlGn"
tmap_arrange(
tm_shape(wetlands_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Wetland"),
